---
title: "Results of the ugodia-types data scrapping"
author: "Eduard Bukin"
date: "`r Sys.Date()`"
output:
  pdf_document: default
editor_options:
  chunk_output_type: console
---



```{r setup, echo = FALSE, warning=FALSE}
library(pacman)
pacman::p_load(sf, here, fs, tidyverse, stringi, jsonlite, 
               httr, RCurl, progress, rgdal, glue, progressr)
force_reharvest <- FALSE
knitr::opts_chunk$set(warning=FALSE, message = FALSE, echo = FALSE)
```


```{r}
ugod_shps <- read_rds(
  here("data-clean", "10.1-sarah-request-clean", "ugodia-geom.rds"))


ray_shps <- read_rds(
  here("data-clean", "02-rayon-shapes", "kaz-rayons-shapes_2021-03-31-13-24-01.rds"))


leg_json <- read_rds(here("data-raw", "19.2-land-ugodia-legend.rds"))
dec_base64_img <- function(encoded_img) {
  tmp_raw_img <- tempfile(fileext = "")
  inconn <- file(tmp_raw_img, "wb")
  writeBin(encoded_img, inconn)
  close(inconn)
  tmp_png_img <- tempfile(fileext = ".png")
  inconn <- file(tmp_raw_img, "rb")
  outconn <- file(tmp_png_img, "wb")
  base64enc::base64decode(what = inconn, output = outconn)
  close(inconn)
  close(outconn)
  tmp_png_img
}



# fill_img <- 
#   leg_json$layers$legend[[1]]$imageData %>%
#   sample(1) %>% 
#   dec_base64_img


```


```{r  echo = FALSE}
ugod_dta <- 
  ugod_shps %>% 
  st_drop_geometry() %>% 
  as_tibble()

ray_dta <- 
  ray_shps %>% 
  st_drop_geometry() %>% 
  as_tibble() %>% 
  filter(raj_rus %in% ugod_dta$raj_rus) %>% 
  mutate(ray_area_ha = shape_area / 10000) %>% 
  select(raj_rus, ray_area_ha)

ugod_legend <-
  leg_json$layers$legend[[1]] %>%
  bind_rows() %>%
  filter(label %in% ugod_dta$USL) 


ugod_legend <-
  leg_json$layers$legend[[4]] %>%
  bind_rows() %>%
  filter(label %in% ugod_dta$USL, !label %in% ugod_legend$label) %>% 
  bind_rows()

ugod_sum <- 
  ugod_dta %>% 
  select(raj_rus, everything()) %>% 
  group_by(raj_rus, USL) %>% 
  summarise(`Ugodia area, HA` = sum(area_ha, na.rm = T)) %>%
  ungroup() %>%
  left_join(ray_dta) %>% 
  mutate(`% share of rayon land` = `Ugodia area, HA` / ray_area_ha * 100) %>% 
  arrange(raj_rus, desc(`% share of rayon land`)) %>% 
  ungroup() 

ugod_only_sum <-
  ugod_sum %>% 
  group_by(USL) %>% 
  summarise(ugod_area = sum(`Ugodia area, HA`, na.rm = T),
            ugod_area_share = ugod_area / sum(ray_dta$ray_area_ha)) %>% 
  ungroup() %>%
  mutate( ugod_area_share_chr = ugod_area_share %>%  scales::percent(0.1)) 
```
 
## Generic data summaries

Data below is presented for 3 rayons.


### Area of each rayon, where we know the types of ugodia

Remaining area is too complex to harvest.

```{r}
ugod_sum %>% 
  group_by(raj_rus, ray_area_ha) %>%
  summarise(
    `Known ugodia area, HA` = sum(`Ugodia area, HA`),
    `% share of rayon land` = sum(`% share of rayon land`)) %>% 
  ungroup() %>% 
  select(Rayon = raj_rus,
         `Rayon area, ha` = ray_area_ha,
         everything()) %>% 
  mutate(across(where(is.numeric), ~scales::comma(., 0.01, big.mark = " "))) %>% 
  knitr::kable(align = "c")
```



### Ugodia that take more than 1% of area in rayon. 

`%` next to each rayon name corresponds to the % of all ugodia that is harvested if we filter only those that take more than 1% of rayon. 

```{r fig.width=10, fig.height=5}
ugod_sum %>%
  filter(`% share of rayon land` > 0.5) %>%
  mutate(USL =
           USL %>% 
           # str_sub(USL, 1, 5) %>% 
           as_factor() %>% 
           fct_reorder(.x = `% share of rayon land`, .desc = T)
         ) %>% 
  group_by(raj_rus) %>% 
  mutate(area_ray_2 =  sum(`% share of rayon land` / 100)  %>%
           scales::percent(0.1)) %>% 
  mutate(raj_rus = str_c(raj_rus, " (", area_ray_2, ")")) %>% 
  ggplot() + 
  aes(y = `% share of rayon land`, x = USL, fill = USL) + 
  geom_bar(stat = "identity") + 
  facet_wrap(. ~ raj_rus, scales = "free_x") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```


```{r fig.height=5, fig.width=10}
space = 4
# devtools::install_github("clauswilke/ggtextures")
library(ggtextures)

layer_dta <-
  ugod_legend %>% 
  # filter(label %in% pull(filter(ugod_sum, `% share of rayon land` > 1), USL)) %>% 
  # group_by(layer_name) %>%
  mutate(values = map_chr(values, ~ {if (is.null(.x)) {""} else {.x}})) %>%
  mutate(
    across(
      c(label, values),
      ~ stringi::stri_trans_general(., "Cyrillic-Latin/BGN") %>%
        stringi::stri_trans_general("Latin-ASCII") %>%
        str_replace_all("[^[:alnum:] ]", "")
    ),
    USL = label,
    label = str_c(label, ". API val: ", values),
    ing_path = map_chr(imageData, dec_base64_img),
    ymin = row_number() * space,
    ymax = ymin + space * 0.9
  ) %>%
  ungroup() %>% 
  left_join(ugod_only_sum, by = "USL") %>% 
  mutate(label = str_c(USL, " (", ugod_area_share_chr, ")"))




# layer_dta %>%
#   filter(ugod_area_share > 0.01) %>%
#   arrange(desc(ugod_area_share)) %>% 
#   mutate(pages = 1) %>%
#   # mutate(pages = row_number() %% 2) %>%
#   group_by(pages) %>%
#   mutate(ymin = row_number() * space,
#          ymax = ymin + space * 0.9) %>%
#   ungroup() %>%
#   ggplot() +
#   aes(
#     xmin = 0,
#     xmax = space * 2,
#     ymin = ymin,
#     ymax = ymax,
#     x = space * 2 * 1.05,
#     y = (ymax - ymin) / 2 + ymin,
#     label = label,
#     image = ing_path
#   ) +
#   geom_textured_rect(img_width = unit(20, "pt"),
#                      fill = "white",
#                      colour = "black") +
#   geom_label(hjust  = "left") +
#   theme_void() +
#   expand_limits(x = c(0, space * 4)) +
#   # facet_wrap(. ~ pages, nrow = 1) +
#   scale_y_continuous(trans = "reverse")
```



### Legend images of all ugodia types that are harvested.

Some legend images are actually identical and are grayed out on the servers of the cadastre. This is a strange behavior, but we will have to guess who is who.

```{r fig.width=16, fig.height=9}
layer_dta %>%
  arrange(desc(ugod_area_share)) %>% 
  # mutate(pages = 1) %>%
  mutate(pages = row_number() %% 3 + 1) %>%
  group_by(pages) %>%
  mutate(ymin = row_number() * space,
         ymax = ymin + space * 0.9) %>%
  ungroup() %>%
  ggplot() +
  aes(
    xmin = 0,
    xmax = space * 2,
    ymin = ymin,
    ymax = ymax,
    x = space * 2 * 1.05,
    y = (ymax - ymin) / 2 + ymin,
    label = label,
    image = ing_path
  ) +
  geom_textured_rect(img_width = unit(20, "pt"),
                     fill = "white",
                     colour = "black") +
  geom_label(hjust  = "left") +
  theme_void() +
  expand_limits(x = c(0, space * 4)) +
  facet_wrap(. ~ pages, nrow = 1) +
  scale_y_continuous(trans = "reverse")
```

### Aggregates of Ugodias types cherry-picked for 3 rayons:

```{r}
ugod_types <-
  tribble(
    ~ USL, ~ ugodia,
    '71732000', "Cropland",
    '71734000', "Hayfield",
    '71735000', "Pasture",
    '71736000', "Pasture on slopes",
    '72110000', "Rocky areas",
    '72120000', "Rocky areas",
    '71111000', "Forests",
    '22520000', 'Permanent snow',
    '22160000', 'Permanent snow',
    '42100000', 'Builtup area'
  )

knitr::kable(ugod_types)
```

### Area of each aggregated ugodia type in all rayons

```{r}
ugod_sum %>% 
  left_join(ugod_types) %>% 
  group_by(ugodia, ray_area_ha, raj_rus          ) %>% 
  summarise(`Ugodia area, HA` = sum(`Ugodia area, HA`)) %>% 
  group_by(ugodia ) %>% 
  summarise(`Ugodia area, HA` = sum(`Ugodia area, HA`),
            `Total area of 3 rayon, ha` = sum(ray_area_ha )) %>% 
  arrange(desc(`Ugodia area, HA`)) %>% 
  mutate(`% share of total land in 3 rayon` = 
           scales::percent(`Ugodia area, HA`  / `Total area of 3 rayon, ha`),
         `Ugodia area, HA` = scales::comma(`Ugodia area, HA`, big.mark = " "),
         `Total area of 3 rayon, ha` = scales::comma(`Total area of 3 rayon, ha`, 
                                                     big.mark = " ")) %>% 
  mutate(ugodia = ifelse(is.na(ugodia), "Other land types", ugodia)) %>% 
  knitr::kable(align = "c")
```



### Area of each known ugodia type in each rayon

```{r}
ugod_sum %>% 
  select(-ray_area_ha ) %>% 
  mutate(across(where(is.numeric), ~scales::comma(., 0.01, big.mark = " "))) %>% 
  knitr::kable(align = "c")
```



## Mapping ugodia types


```{r  fig.width=16, fig.height=7}
simple_shapes <- 
  ugod_shps %>% 
  # st_simplify(preserveTopology = T)
  # st_drop_geometry() %>% 
  left_join(ugod_sum, by = c("USL", "raj_rus")) %>% 
  # filter(`% share of rayon land` > 1) %>% 
  st_simplify(preserveTopology = T)




simple_shapes$raj_rus %>%
  unique() %>%
  walk( ~ {
    ray_dta <-
      simple_shapes %>%
      # st_drop_geometry() %>%
      filter(str_detect(raj_rus, .x))
    out_plot <- 
      ggplot() +
      aes(fill = USL) +
      geom_sf(
        mapping = aes(fill = "Not harvested"),
        data =
          filter(ray_shps, raj_rus  %in% ray_dta$raj_rus) %>%
          mutate(
            USL = "Not harvested",
            `% share of rayon land` = 100 - sum(unique(ray_dta$`% share of rayon land`))
          ) ,
        inherit.aes = T,
        fill = "black",
        colour = "black"
      ) +
      geom_sf(
        data = ray_dta %>%
          mutate(
            USL =
              USL %>%
              str_c(" (", scales::comma(`% share of rayon land`), "%)") %>%
              # str_sub(USL, 1, 5) %>%
              as_factor() %>%
              fct_reorder(.x = `% share of rayon land`, .desc = T)
          ) ,
        colour = NA
      ) +
      labs(title = unique(ray_dta$raj_rus),
           caption = "Not harvested area is in black") +
      theme_minimal()
    plot(out_plot)
  })


```









