---
title: "Reclassification of plot purposes"
author: "Eduard Bukin"
date: "8/4/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---


```{r setup}
library(pacman)
pacman::p_load(sf, tidyverse, rgdal, rmapshaper, mapview, here, tidytext,
               knitr, kableExtra)
```

```{r}
plots_ugods_geoms <- read_rds("data-clean/10.1-sarah-request-clean/plot-geom-ugod-areas.rds") 
```


## Main goal

We attempt to reclassify free-text 'celevoe naznachenie' into the more interpretable categories. We do so in the following way:

1. Select 3 columns: plot ID, Naznachenie and Area of the plot.
2. Do some basic semantic analysis of the words. 
3. Use `str_detect()` and some conditional statements to reclassify the actual celevoe naznachenie.
4. Check frequencies of different "celevoe naznachenie" in each classified category.
5. `left_join()` new classification to the plots geometries and resave the data.


### Steps 1 and 2:

There are quite some words in here. 

```{r}
ugod_mtdt_df <- 
  plots_ugods_geoms %>% 
  st_drop_geometry() %>% 
  as_tibble() %>% 
  select(cadastre_id, cel_nazn = meta_rus_celevoe_naznacenie, 
          cel_nazn_kaz = meta_kaz_celevoe_naznacenie, area_ha ) 

# Checking words frequency
ugod_mtdt_df %>% 
  unnest_tokens(word, cel_nazn) %>%
  count(word, sort = TRUE) %>% 
  kable(format = "html") %>% 
  scroll_box(height = "500px", fixed_thead = T)

# Checking words frequency
ugod_mtdt_df %>% 
  unnest_tokens(word, cel_nazn_kaz) %>%
  count(word, sort = TRUE) %>% 
  kable(format = "html") %>% 
  scroll_box(height = "500px", fixed_thead = T)
```


### Step 3

New variable "new_nazn" correspond to the new classification.

```{r}
plot_naznachenie <- 
  ugod_mtdt_df %>% 
  mutate(
    new_nazn = NA_character_,
    cel_nazn = str_to_lower(cel_nazn),
    new_nazn =
      case_when(
        is.na(new_nazn) & 
          (
            str_detect(cel_nazn, "podsobno|obnogo|podsosbnogo|podsobonogo|podsobngo|podsounogo") &
              !str_detect(cel_nazn, "pomesenie") |
              (str_detect(cel_nazn, "licn") & !str_detect(cel_nazn, "teplic") & 
                 str_detect(cel_nazn, "hozaj"))
          ) ~ "ag_hh_podsob",
        
        is.na(new_nazn) & (
          str_detect(cel_nazn, "krest|fermers|kroest|kreas|kores|korest")
        ) ~ 
          "ag_IF_krest",
        
        is.na(new_nazn) & 
          (
            str_detect(cel_nazn, "sadovod|sadav|sadoa|sadov|saadov|sada|sadlov|sadorv") &
              !str_detect(cel_nazn, "detskog")
            ) ~ 
          "ag_gardens",
        
        is.na(new_nazn) & 
          (
          str_detect(cel_nazn, "tovarnogo|tovarn|too|pred|firm|teplic|tiplic") | 
          (str_detect(cel_nazn, "veden") & str_detect(cel_nazn, "hozaj") &
             !str_detect(cel_nazn, "ohotn")) 
        ) ~ 
          "ag_prod",
        
        is.na(new_nazn) & (
          str_detect(cel_nazn, "selsko") & 
          !str_detect(cel_nazn, "obslu|ustanov|klub|maga|obsz") |
          str_detect(cel_nazn, "vypasa|skota") |
          str_detect(cel_nazn, "ohotn")
        ) ~ 
          "ag_other",
        
        is.na(new_nazn) & (
          str_detect(cel_nazn, "stroitel") &
            !str_detect(cel_nazn, "npp|park|prirod")
          ) ~ 
          "noag_const",
        
        is.na(new_nazn) & (
          str_detect(cel_nazn, "bsluz|magazi|ustanov|klub|razmes|kompl|obsz|oblsluz") &
            !str_detect(cel_nazn, "npp|park|prirod")
        ) ~ 
          "noag_service",
        
        is.na(new_nazn) & (
          str_detect(cel_nazn, "ohotnic")
        ) ~ 
          "other_other", #"other_hunting",
        
        is.na(new_nazn) & (
          str_detect(cel_nazn, "npp|prirod") 
        ) ~
          "other_protected", #"other_forest",
        
        is.na(new_nazn) & (
          str_detect(cel_nazn, "lesnogo|leso") 
        ) ~
          "other_forest", #"other_forest",
        
        is.na(new_nazn) & (
          str_detect(cel_nazn, "forele|rybno|prudov")
        ) ~ 
          "other_fish", #"other_fish",
        
        TRUE ~ "other_other"
      )
  )

```


### Step 4. Checking quality of classification


#### All categories at once

```{r}
plot_naznachenie %>%
  count(new_nazn, cel_nazn, cel_nazn_kaz) %>%
  arrange(new_nazn, desc(n)) %>%
  DT::datatable(fillContainer = T, options = list(paging = FALSE), height = "500px") %>% 
  htmltools::div(height = "500px")
```


#### By each category

```{r echo=FALSE}
plot_naznachenie$new_nazn %>%
  unique() %>%
  sort() %>% 
  map(~{
    htmltools::tagList(
      htmltools::h5(.x),
      plot_naznachenie %>%
        filter(new_nazn ==  .x) %>%
        count(new_nazn, cel_nazn, cel_nazn_kaz) %>%
        arrange(new_nazn, desc(n)) %>%
        DT::datatable(fillContainer = T, options = list(paging = FALSE))
    )
    # cat("####", .x, "\n\n\n\n")
    #  %>%
    #   knit_print()
    # cat("\n\n\n\n")
  }) %>% 
  htmltools::tagList()
```


#### Visualising everything 

```{r eval = FALSE}
# plots_ugods_geoms_simplified <-
#   plots_ugods_geoms %>%
#   # st_drop_geometry() %>% 
#   # as_tibble() %>% 
#   # mutate(group = sort(row_number() %% 3)) %>%
#   group_by(rayon_id) %>% 
#   nest() %>% 
#   mutate(data = map(data, ~ {
#     cat("new group \n\n")
#     rmapshaper::ms_simplify(.x, keep = .05, keep_shapes = T)})) %>% 
#   ungroup() %>% 
#   # select(-group) %>% 
#   unnest()
# object.size(plots_ugods_geoms_simplified) / 1024 / 1024
# object.size(plots_ugods_geoms) / 1024 / 1024
# plots_ugods_geoms_simplified %>% write_rds("data-temp/plots_ugods_geoms_simplified.rds", compress = "gz")
# plots_ugods_geoms_simplified <- read_rds("data-temp/plots_ugods_geoms_simplified.rds")

# out_map <-
#   plots_ugods_geoms %>%
#   st_as_sf() %>%
#   left_join(plot_naznachenie %>% select(cadastre_id , new_nazn), by = "cadastre_id") %>%
#   # filter(!str_detect(new_nazn, "noag_")) %>%
#   select(cadastre_id, new_nazn, contains("meta_")) %>%
#   mapview(., zcol = "new_nazn", burst	= TRUE)
# mapshot(out_map, url = "data-clean/10.1-sarah-request-clean/plot-new-class.html")
```


### Step 5. Saving results into a new file


```{r warning=FALSE}
plot_naznachenie %>% 
  write_rds("./data-clean/10.1-sarah-request-clean/plot-celevoe-naznac-reclass.rds", compress = "gz")

plots_ugods_geoms2 <-
  plots_ugods_geoms %>%
  left_join(plot_naznachenie %>% select(cadastre_id , new_nazn), by = "cadastre_id") %>%
  select(cadastre_id, new_nazn, everything())

plots_ugods_geoms2 %>%
  write_rds(
    "./data-clean/10.1-sarah-request-clean/plot-geom-ugod-areas-naznac-reclass.rds",
    compress = "gz"
  )

plots_ugods_geoms2 %>% 
  st_write(
    here(
      "data-clean",
      "10.1-sarah-request-clean",
      "plot-geom-ugod-areas-naznac-reclass-shp",
      "plot-geom-ugod-areas-naznac-reclass.shp"
    ), 
    delete_layer = TRUE
  )

plots_ugods_geoms3 <-
  read_rds("data-clean/10.1-sarah-request-clean/plot-fractions-ugod-all-geom.rds") %>%
  left_join(plot_naznachenie %>% select(cadastre_id , new_nazn), by = "cadastre_id") %>%
  select(cadastre_id, ugodia, plot_class = new_nazn, contains("area"), everything()) %>% 
  mutate(plot_class_ugodia = str_c(plot_class, " - ", ugodia))

plots_ugods_geoms3 %>%
  write_rds(
    "./data-clean/10.1-sarah-request-clean/plot-fractions-ugod-all-naznac-reclass.rds",
    compress = "gz"
  )

plots_ugods_geoms2 %>% 
  st_write(
    here(
      "data-clean",
      "10.1-sarah-request-clean",
      "plot-fractions-ugod-all-naznac-reclass-shp",
      "plot-fractions-ugod-all-naznac-reclass.shp"
    ), 
    delete_layer = TRUE
  )

# out_map2 <-
#   plots_ugods_geoms3 %>%
#   mapview(., zcol = "plot_class_ugodia", burst	= TRUE)
# mapshot(out_map2, url = "data-clean/10.1-sarah-request-clean/ugod-plot-new-class.html")
```

